---
title: "Supplementary Materials: SUggestions from Reviewers"
author: "Alasdair D.F. Clarke and Anna E. Hughes"
date: "2023-03-24"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.height = 3,
  fig.align = "center")
```

# Introduction

```{r load-packages, include = FALSE}
library(tidyverse)
library(brms)
library(tidybayes)
library(patchwork)
library(latex2exp)
library(ggpmisc)
library(ggridges)
library(corrr)
library(knitr)
library(kableExtra)
```

```{r}
# set ggplot2 theme
theme_set(ggthemes::theme_tufte())
colourPalette <- c("#e78429", "#ed968c", "#7c4b73","#aadce0", "#72bcd5", "528fad")

# use parallel cores for mcmc chains!
options(mc.cores = 4)

# reduce the number of decimal places
options(digits = 3)

# functions used for our Bayesian re-analysis
source("../scripts/our_functions.R")

# set seed to make sure everything is reproducible 
set.seed(100320021)
```


Here we present two additional analysis that were suggested during the Stage Two peer review process. We thank the reviewers for their suggestions. 

# Effect of block on correlations

In `4_Planned_Explorations` we reported that \ldots. 

During peer review it was suggested that we could partially disentangle contributions of feature type and block from one another by looking at how the correlations change within sub-blocks. <EXPAND>. 

If the correlation results are primarily being driven by block, then we could expect to see a decreases in the correlation over sub-blocks. Whereas if it is down to the difference in colour v shape features.


## Import Data

As this analysis was not originally planned, sub-block was not saved, stored and calculated in our original pre-processing pipeline. But, we can re-import and reconstruct it here!

```{r cache=TRUE, warning = FALSE}

d <- read_csv("../../data/main/accuracy_rt_data.txt", show_col_types = F) %>%
  mutate(
         colour = as_factor(feature),
         nd = distractor_no) %>%
  select(observer, experiment = "block", colour, nd, accuracy, rt)
```

First check that all the `1b` trials are clumped together in their own block:

```{r}

d %>% mutate(n = 1:n()) %>% 
  filter(experiment == "1b") 
```

These all seem to be consecutive, so we can remove them.

```{r}
d <- filter(d, experiment != "1b")

# now check we have even trials per person!
d %>% group_by(observer) %>%
  summarise(n = n()) %>%
  summarise(unique_n = unique(n))
```
Trials where presented in sub-blocks of 320 trials, so let us reconstruct that!

```{r}
d %>% group_by(observer) %>%
  mutate(trial = 1:n(),
         block = ceiling(trial/320)) -> d
```


Now carry out the rest of our original pre-processing (exactly as before)

```{r}
summary(d)

```

